Fluid structure interaction with ETVF

### 2021-10-31 manuscript/paper.tex
Updates files according to paper.

\subsection{Elastic bar hanging under gravity}
\label{sec:elastic-bar-hanging}

Currently this is a sub problem of elastic dam break. In that problem we are
simulating gate with out considering the gravity. By considering the gravity
we get float division error.

@@

Taken from \citet{sun2019fully}.

@@

In this example the elastic plate is placed at the end. Which gets
impacted due to the moving fluid. Further information can be found at
section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.

\subsection{Water slamming on a sandwich hull}
\label{sec:water-slamming-on-a-sandwich-hull}

>>>>

@@

Taken from \citet{sun2019fully, ng2020coupled}.

@@

In this example the elastic plate is placed at the end. Which gets impacted
due to the moving fluid. Further information can be found at section 3.2 of
\cite{liu2013numerical}, \citet{sun2019fully}, {A $\delta$ SPH-SPIM coupled
  method for fluid-structure interaction problems}.
